%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
%\documentclass[smallextended]{svjour3}       % onecolumn (second format)
\documentclass[smallextended,natbib]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%
% Insert the name of "your journal" with
% \journalname{myjournal}
%

%%%
\begin{document}

\section*{Short biographies of authors}
\begin{description}

% correct the CV
\item[Thieu Nguyen (BS.c)]				% ORCID 0000-0001-9994-8747
received his university degree from the School of Information and Communication Technology, Hanoi University of Science and Technology (the ICT Talented Engineering program). In 2013, he was awarded the Third Prize in Mathematical Competition for High School students at the provincial level. In recent two years, he contributes as the first author to several papers in international conferences with research topics focused on intelligent methods using neural networks and meta-heuristic algorithms for proactive forecasting in cloud resource management. 


% correct the CV
\item[Tu Nguyen (Mr.)]						% ORCID 0000-0003-3992-7367
is a student at School of Information and Communication Technology, Hanoi University of Science and Technology (Vietnam). In 2015 he won the First Prize of the Online Math Competition, the Second Prize in solving math using calculator organized by BITEX, and the Second Prize in Physics Competition for High School in his province. In 2016, he received the Hoa Trang Nguyen award for students with top-score in the national university entrance examination. He is interested in high performance computing, artificial intelligence and data analytics. 


\item [Binh-Minh Nguyen (Dipl. Eng., Ph.D.)] 	% ORCID: 0000-0003-1328-3647
received his Dipl. Eng. degree in Computer Aided Design from the Institute of Automation and Information Technologies, Tambov State Technical University (Russia) in 2008 and his Ph.D. degree in Applied Informatics from the Faculty of Informatics and Information Technology, Slovak University of Technology (STU) in Bratislava (Slovakia) in 2013. Since 2008 to 2013, he worked as researcher at the Institute of Informatics, Slovak Academy of Sciences (IISAS), Slovakia. Currently, he is a lecturer, scientific researcher at the School of Information and Communication Technology, Hanoi University of Science and Technology (Vietnam). His research interests include cloud computing and scalable engineering, Blockchain, Internet of Things, distributed systems, and data analytics.


\item[Giang Nguyen (M.Sc., Ph.D.)]			% ORCID 0000-0002-6769-0195
is a senior researcher at the Institute of Informatics, Slovak Academy of Sciences (IISAS) with research topics focused on soft computing, scalable data and knowledge technologies with high performance backgrounds. She received M.Sc. degree in Informatics and Information Technology, Ph.D. degree in Applied Informatics from the Slovak University of Technology (STU) in Bratislava, Slovakia. She is (co-)author of scientific papers and has been participating in EU IST RTD, EU H2020 and national projects. She is a member of the IISAS scientific board, program committees and reviewer for scientific journals, international conferences and national proposals. She is also a supervisor for PhD. study at the IISAS and STU in Bratislava, Slovakia.


 
\end{description}

\end{document}
